\subsection{The Vehicle Service}\label{subsec:vehicleservice}

The \code{VehicleService} is responsible for persisting the objects of the type \code{Vehicle} and their related \code{VehicleIcon}.

An overview of the end--points in the \code{VehicleService} are listed in \cref{table:endpointvehicleservice}.
This service has mostly generic functionality, i.e. get all vehicles, add vehicle, get by id, and update by id.
However it also has the ability to get and update an icon.
This icon is for the consumer client to use as a ``profile picture'' for vehicles.
This behavior is shared with the \code{UserService} in which the same occurs for users.

\subimport{memes}{vehicle_overview_table.tex}

For vehicles their \acp{VIN} are unique, this should be enforced in the service.
We do this when new vehicles are created or old vehicles are modified.
The code used when creating new vehicles are shown in \cref{lst:vehicleservicevincheck}.
First we check if the \ac{VIN} present on the \code{VehicleBuilder} is not null,
such that we can use the \code{VehicleDao} to check if the \ac{VIN} is already in use.
If it is already in use then an error should be given, here we throw a custom exception,
\code{ConflictException}, this sets the HTTP status code to ``409 Conflict'', and returns the message as JSON.

\begin{listing}
    \begin{java2}
if (vehicleBuilder.getVin() != null && vehicleDao.byVin(vehicleBuilder.getVin()) != null) {
    throw new ConflictException("A vehicle with that Vin already exists.");
}
    \end{java2}
    \caption{Test to see if Vin is already in database.}\label{lst:vehicleservicevincheck}
\end{listing}
