\subsection{Effects}\label{subsec:testeffects}
The following points present our findings during system and load testing, and how we tried to mend found faults:
\begin{description}
    \item[Consistency Errors]\hfill \\
        As presented in \cref{subsec:nosql_vs._sql}, we discovered that our first choice of database system type, NoSQL, and especially its implementation through Hibernate OGM, behaved faulty under load.
        The error occurred when two objects were being created at the same time, partly because Hibernate OGM's way of requiring unique ids was not thread safe.
        This meant that we had to change our persistence layer in order to establish consistent data handling.

        Another consistency error found, was that sometimes two different drivers would be made for the same user, something which should not be allowed in our system.
        This error was caused by a fault where the same user would create two routes simultaneously, while having no existing driver, thus resulting in a race condition creating two different drivers.
        Fortunately, this error will never present itself in daily use of our system, since a given user is assigned a driver the first time he/she creates a route;
        and a real user should only be used by one person, thus making it improbable that two separate routes are created at the exact same time.

        After discovering that creating two or more routes for the same user at the same time, could lead to this error, we changed the test plan to reflect the real world more accurately by ensuring that all routes, created simultaneously are done so by a unique user.
    \item[High Response Times]\hfill \\
        When we switched from a NoSQL to SQL database system, we expected to get faster performance throughout the system, because in the NoSQL database we had to aggregate a lot of documents to use the data, which now could be done using joins in the SQL database.
        However, this was the not case, and our new SQL database system had unsatisfactory performance under load, i.e.~nearly identical to the previous NoSQL database system.

        We then introduced indices in our SQL database system, which meant that fetching elements, something that Hibernate ORM does every time an existing object is changed, was significantly faster.
    \item[Persistence Errors]\hfill \\
        As previously mentioned our choice of a NoSQL database system resulted in some faults, which were discovered during system test.
        Most of these faults were due to the Hibernate OGM implementation, which we found unstable.
        One fault was that an object could not be fetched twice in the same entity manager context, meaning that we could now use an object found earlier in the same \enquote{transaction}.
        Another fault proved even more severe, and resulted in the group submitting a bug report to the official Hibernate OGM codebase, which was later recognised by the Hibernate team.
        The fault meant that objects inserted during a transaction could not be changed later in the transaction.

        The discovering of these faults aided our decision to change to an SQL database system and thus Hibernate ORM.
\end{description}
